Earth at night*\\ {\footnotesize \textsuperscript{*}The visualisation of average radiance in specific area}

### 2021-09-05 paper/main.tex
fix ieee format
paper

\usepackage[T1]{fontenc} 
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx} 
\usepackage{textcomp}
\usepackage{xcolor} 
\bibliographystyle{IEEEtran} 
\usepackage[backend=bibtex,doi=true, natbib=true ]{biblatex}
\addbibresource{main.bib}

@@

\begin{abstract}
This document is the description about the solution of Assignment 2 of Compx527 paper in Waikato University. World Bank Nightime Light Data consists of a lot of satellite imagery from the Visible Infrared Imaging Radiometer Suite Day-Night Band (VIIRS DNB) from 2012-2020. We choose 3 specific areas all over the world and focus on the imagery of these places. From these imagery, we can learn the trend of their radiance in the period. Some articles shows that the night light represents the development in the same area. We can preview the economic development of areas by the trend. 
\end{abstract}

@@

\section{Solution Summary}
A lot of things are depended by our project. It is important that imagery from AWS open datasets has almost not processed too much before storing. So we have to spend too much time on the data. To ensure our project development, we use Lark, which is a kind of instant messenger in China used in office, to record documents and communicate in a group. A sumary about our solution is shown as below.

@@

\subsection{ansible}
Ansible is a famous open source deployment platform. Most of services in AWS can be working rightly with Ansible. We used it for our main sctructure deployment.

>>>>

\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx} 
\usepackage{textcomp}
\usepackage{xcolor} 
\usepackage[backend=biber]{biblatex}
\addbibresource{main.bib}

@@

\begin{abstract}
This document is the description about the solution of Assignment 2 of Compx527 paper in Waikato University. World Bank Nightime Light Data consists of a lot of satellite imagery stored in Amazon Web Services (AWS). Recent files from 2012-2020 are generated by the sensors named Visible Infrared Imaging Radiometer Suite Day-Night Band (VIIRS DNB). All the things are stored by Cloud Optimized GeoTIFF (COG) format and organized by Spatial Temporal Asset Catalog (STAC) standard. This project only researches the imagery from 3 specific areas. From them, you can learn the trend of their radiance in the period. It is also a good chance to have a better understanding of ecnomic trend by them. 
\end{abstract}

@@

\section{Solution Summary}
A lot of services are depended by this project. It is important to know that imagery from AWS open datasets has almost not processed too much before storing. So the Geospatial Data Abstraction Library (GDAL) is imported for the complicated computing. In addition, to ensure our project development schedule, Lark, which is a kind of instant messenger used in Chinese office, is used to record documents and communicate in a group. The architecture of our solution is shown as below.

\begin{figure}[htbp]
    \centerline{\includegraphics[width=260pt]{images/arch.png}}
    \caption{Architecture}
    \label{fig1}
\end{figure}

Figure Labels: To process the S3 data, two Lambda functions are generated. One is to follow the STAC protcol to find the imagery, and another is to analyse the picture by GDAL, which is a kind of high cost computation. There are more than 4 pictures per day per area, and more than 5,000 pictures per month totally. All the result processed by Lambda is stored in RDS and synced from us-east-1 region to ap-southeast-1 region. In addition, the password of MySQL are generated by a Lambda function and rotated timely. So the development team do not need to copy the password. Any feature with the password have to get it from Secrets Manager.

When it comes to show the result in ap-southeast-1 region, networking security is the most essential thing because this part of service can be touched by end users. So except ELB server and deployment server, there are not any other servers with public ip. All the EC2 can visit public network from the NAT, but public network can not visit them directly.

@@

\subsection{ansible}
Ansible is a famous open source deployment platform.
